The \dealii Library, Version 9.7

### 2025-07-14 9.7/paper.tex
Describe MappingP1.
It is a nice simplex feature!

>>>>

\subsection{The \texttt{MappingP1} class}
\dealii has supported simplex and mixed meshes since the 9.3
release~\cite{changes93}. That release included \texttt{MappingFE}, a
\texttt{Mapping} class which works with a variety of different elements by
delegating most computations to a provided \texttt{FiniteElement} class. This
release includes a new \texttt{MappingP1} class, which contains an optimized
implementation of the standard affine simplex mapping (i.e., the mapping from
the unit to real cell with a constant Jacobian on each cell). This
implementation is about six times faster than the generic one implemented in
\texttt{MappingFE}. In addition, this \texttt{Mapping} is now the default linear
mapping returned by \texttt{ReferenceCell::get\_default\_linear\_mapping()}, so
all applications which use that function for obtaining a
\texttt{ReferenceCell}-independent mapping will automatically use the more
performant class.
